Strong coupling between scales in a multi-scalar model of urban dynamics

### 2021-01-31 Docs/Papers/Multiscale/paper/paper.tex
arxiv

\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{multirow}

\title{Strong coupling between scales in a multi-scalar model of urban dynamics}

\author{Juste Raimbault$^{1,2,3,\ast}$\medskip\\
$^{1}$ Center for Advanced Spatial Analysis, University College London\\
$^{2}$ UPS CNRS 3611 ISC-PIF\\
$^{3}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\medskip\\
$^{\ast}$ \texttt{juste.raimbault@polytechnique.edu}
}

\date{}

\begin{document}

\maketitle

\begin{abstract}
	Urban evolution processes occur at different scales, with intricate interactions between levels and relatively distinct type of processes. To what extent actual urban dynamics include an actual strong coupling between scales, in the sense of both top-down and bottom-up feedbacks, remains an open issue with important practical implications for the sustainable management of territories. We introduce in this paper a multi-scalar simulation model of urban growth, coupling a system of cities interaction model at the macroscopic scale with morphogenesis models for the evolution of urban form at the scale of metropolitan areas. Strong coupling between scales is achieved through an update of model parameters at each scale depending on trajectories at the other scale. The model is applied and explored on synthetic systems of cities. Simulation results show a non-trivial effect of the strong coupling. As a consequence, an optimal action on policy parameters such as containing urban sprawl is shifted. We also run a multi-objective optimization algorithm on the model, showing showing that compromise between scales are captured. Our approach opens new research directions towards more operational urban dynamics models including a strong feedback between scales.
	\medskip\\
\textbf{Keywords: } Urban dynamics; Systems of cities; Urban morphogenesis; Multi-scalar modeling; Strong coupling
\end{abstract}

%  relevant target CEUS? https://www.elsevier.com/journals/computers-environment-and-urban-systems/0198-9715/guide-for-authors => special issue expired; IJGI 31/01:  https://www.mdpi.com/journal/ijgi/special_issues/spatio_temporal_models_geo

% Systems of cities
%Multi-scalar model
%Spatial interaction
%Reaction-diffusion

% abstract CCS
% 
%The modeling of urban growth is a crucial issue for the design of sustainable territorial policies, through the understanding of past urbanization processes and the forecasting of future urban trajectories. Several models have been proposed at different scales and integrating differ- ent dimensions of urban systems, such as land-use transport interaction models [1] or systems of cities models [2]. While multi-scalar models are recognized as crucial for the study of such systems [3], they remain in practice unexplored.
%This contribution introduces a parsimonious multi-scalar model for systems of cities, based on simple dimensions (mainly populations) with stylized processes, but yielding an effective strong coupling between the metropolitan mesoscopic scale and the macroscopic scale of the system of cities. The model couples the spatial interaction model of [4] for the macro scale with the reaction-diffusion model for urban form studied by [5]. More precisely, urban areas viewed as a population grid are embedded into the macroscopic interaction model. To evolve populations and local urban forms, one time step consists of (i) population differences are computed by the interaction model; (ii) top-down feedback modifies parameters of mesoscopic models, given control parameters to capture typical scenarios (transit-oriented development or sprawl for diffusion, metropolization or uniformization for aggregation); (iii) local urban form are evolved with the reaction-diffusion models at a given speed conditionally to the population variations; (iv) changes in urban form influence macroscopic interaction ranges (capturing the impact of local activity on global insertion), by integrating gravity flows in the area with a squared cost function making a compromise between congestion and flows.
%The model is applied on synthetic systems of cities typical of a continental range (500km, hierarchy around 1, 20 cities), with initial local population grid configurations as monocen- tric. Parameter space is explored with the OpenMOLE model exploration software [6], eased by the implementation of the model in scala [7]. First results show a strong impact of the strong meso-macro coupling, such as for example a qualitative inversion of the behavior as a function of interaction range of macroscopic indicators trajectories when switching from a “transit-oriented development” scenario (negative feedback of population growth on diffusion) to a “sprawl” scenario (positive feedback). Similarly, mesoscopic urban form indicators are significantly influenced by the coupling process.
%Further work will consist in more targeted simulation experiments, including specific ex- ploration algorithms such as diversity search for model regimes [6], to test the model as a proof-of-concept of models for policies. Such a model can also be calibrated on real city sys- tems and urban form trajectories, to extrapolate coupling parameters that would be difficult to obtain otherwise. Our contribution is thus a first step towards multi-scalar simulation models for systems of cities.

% multilevel models : check https://scholar.google.fr/citations?user=x1BwVXoAAAAJ&hl=fr
% + Morvan, G. (2014). Bibliographic database on multi-level and multi-scale agent-based modeling. Transportation Research Procedia, 2, 495-500.

%\cite{louail2010comparer}

@@

\begin{figure}
%  figure: more details?
 \includegraphics[width=\linewidth]{multiscale_morph.pdf}
 \caption{Schematic representation of model architecture. Urban areas with their own urban form are inserted into the macroscopic spatial interaction model, and strong coupling is achieved through top-down and bottom-up feedbacks.\label{fig:fig1}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{allindics_hist.png}
	\caption{Statistical distribution of indicators for a sample of 10 parameter values.\label{fig:fig2}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{onefactor_allindics_mesoMacroDecayUpdateMax_errorbars.png}
	\caption{Variations of indicators as a function of $\delta d$, when all other parameters are fixed to their nominal value.\label{fig:fig3}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{deltaHierarchymacroPopulations-mesoTimeSteps_colorMacroInteractionDecay_facetmesoMacroDecayUpdateMax-macroMesoBetaUpdateMax.png}
	\caption{Macroscopic hierarchy of populations as a function of mesoscopic time steps $t_m$, for different values of interaction decay $d_G$ (colour), and of feedback parameters $\delta d$ (columns) and $\delta \beta$ (rows).\label{fig:fig4}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{deltamesoMorans-macroMesoAlphaUpdateMax_colormacroMesoBetaUpdateMax_facetmesoMacroCongestionCost-mesoMacroDecayUpdateMax_mesoBeta0_11.png}
	\caption{Relative evolution of average mescoscopic Moran, as a function of feedback parameter $\delta \beta$, for different values of feedback parameter $\delta \alpha$ (colour), and of feedback parameters $\delta d$ (columns) and $\lambda$ (rows).\label{fig:fig5}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\textwidth]{deltamesoSlopes-macroMesoAlphaUpdateMax_colormacroMesoBetaUpdateMax_facetmesoMacroCongestionCost-mesoMacroDecayUpdateMax_mesoBeta0_11.png}
	\caption{Relative evolution of average mescoscopic population hierarchy, as a function of feedback parameter $\delta \beta$, for different values of feedback parameter $\delta \alpha$ (colour), and of feedback parameters $\delta d$ (columns) and $\lambda$ (rows).\label{fig:fig6}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
	\includegraphics[width=0.6\linewidth]{pareto_macroHierarchy-mesoHierarchy.png}
	\end{center}
	\caption{Pareto front obtained with a NSGA2 genetic algorithm, to minimize simultaneously hierarchy at the macroscopic and mesoscopic scales. Point size gives the number of stochastic samples and colour the value of $\delta \beta$.\label{fig:fig7}}
\end{figure}

@@

% conclusion not needed
%\section{Conclusion}
%This paper provides a first step towards strongly multi-scalar models to capture urban complexity towards policy models. 
%Towards integrative models and theories for urban systems \cite{raimbault2019methods}

\section*{Acknowledgments}

The author acknowledges the funding of their institutions and the EPSRC project number EP/M023583/1. Results obtained in this paper were computed on the vo.complex-system.eu virtual organisation of the European Grid Infrastructure (http://www.egi.eu). We thank the European Grid Infrastructure and its supporting National Grid Initiatives (France-Grilles in particular) for providing the technical support and infrastructure.

\begin{thebibliography}{}

\bibitem[Banos et~al., 2015]{banos2015importance}
Banos, A., Corson, N., Gaudou, B., Laperri{\`e}re, V., and Coyrehourcq, S.~R.
  (2015).
\newblock The importance of being hybrid for spatial epidemic models: a
  multi-scale approach.
\newblock {\em Systems}, 3(4):309--329.

\bibitem[Batty, 2005]{batty2005agents}
Batty, M. (2005).
\newblock Agents, cells, and cities: new representational models for simulating
  multiscale urban dynamics.
\newblock {\em Environment and Planning A}, 37(8):1373--1394.

\bibitem[Batty, 2018]{batty2018inventing}
Batty, M. (2018).
\newblock {\em Inventing future cities}.
\newblock MIT press.

\bibitem[Bedau, 2002]{bedau2002downward}
Bedau, M. (2002).
\newblock Downward causation and the autonomy of weak emergence.
\newblock {\em Principia: an international journal of epistemology},
  6(1):5--50.

\bibitem[Belem and M{\"u}ller, 2013]{belem2013organizational}
Belem, M. and M{\"u}ller, J.~P. (2013).
\newblock An organizational model for multi-scale and multi-formalism
  simulation: Application in carbon dynamics simulation in west-african
  savanna.
\newblock {\em Simulation Modelling Practice and Theory}, 32:83--98.

\bibitem[Boulet et~al., 2020]{boulet2020coupling}
Boulet, X., Zargayouna, M., Scemama, G., and Leurent, F. (2020).
\newblock Coupling multi-agent and macroscopic simulators of traffic.
\newblock In {\em Agents and Multi-agent Systems: Technologies and Applications
  2019}, pages 323--332. Springer.

\bibitem[Chavalarias et~al., 2009]{chavalarias2009french}
Chavalarias, D., Bourgine, P., Perrier, E., Amblard, F., Arlabosse, F., Auger,
  P., Baillon, J.-B., Barreteau, O., Baudot, P., Bouchaud, E., et~al. (2009).
\newblock French roadmap for complex systems 2008-2009.

\bibitem[Cheng and Masser, 2003]{cheng2003modelling}
Cheng, J. and Masser, I. (2003).
\newblock Modelling urban growth patterns: a multiscale perspective.
\newblock {\em Environment and Planning A}, 35(4):679--704.

\bibitem[Clarke et~al., 2007]{clarke2007decade}
Clarke, K.~C., Gazulis, N., Dietzel, C., and Goldstein, N.~C. (2007).
\newblock A decade of sleuthing: Lessons learned from applications of a
  cellular automaton land use change model.
\newblock {\em Classics in IJGIS: twenty years of the international journal of
  geographical information science and systems}, pages 413--427.

\bibitem[Crociani et~al., 2016]{crociani2016multi}
Crociani, L., L{\"a}mmel, G., and Vizzari, G. (2016).
\newblock Multi-scale simulation for crowd management: a case study in an urban
  scenario.
\newblock In {\em International Conference on Autonomous Agents and Multiagent
  Systems}, pages 147--162. Springer.

\bibitem[Favaro and Pumain, 2011]{favaro2011gibrat}
Favaro, J.-M. and Pumain, D. (2011).
\newblock Gibrat revisited: An urban growth model incorporating spatial
  interaction and innovation cycles.
\newblock {\em Geographical Analysis}, 43(3):261--286.

\bibitem[Ford et~al., 2019]{ford2019multi}
Ford, A., Barr, S., Dawson, R., Virgo, J., Batty, M., and Hall, J. (2019).
\newblock A multi-scale urban integrated assessment framework for climate
  change studies: A flooding application.
\newblock {\em Computers, Environment and Urban Systems}, 75:229--243.

\bibitem[Gabaix, 1999]{gabaix1999zipf}
Gabaix, X. (1999).
\newblock Zipf's law for cities: an explanation.
\newblock {\em Quarterly journal of Economics}, pages 739--767.

\bibitem[Hjorth et~al., 2020]{hjorth2020levelspace}
Hjorth, A., Head, B., Brady, C., Wilensky, U., et~al. (2020).
\newblock Levelspace: A netlogo extension for multi-level agent-based modeling.
\newblock {\em Journal of Artificial Societies and Social Simulation},
  23(1):1--4.

\bibitem[James et~al., 2018]{james2018zipf}
James, C., Azaele, S., Maritan, A., and Simini, F. (2018).
\newblock Zipf's and taylor's laws.
\newblock {\em Physical Review E}, 98(3):032408.

\bibitem[Joy and Vogel, 2015]{joy2015toronto}
Joy, M. and Vogel, R.~K. (2015).
\newblock Toronto’s governance crisis: A global city under pressure.
\newblock {\em Cities}, 49:35--52.

\bibitem[Liao and Gaudin, 2017]{liao2017ouverture}
Liao, L. and Gaudin, J.-P. (2017).
\newblock L’ouverture au march{\'e} en chine (ann{\'e}es 1980-2000) et le
  d{\'e}veloppement {\'e}conomique local: une forme de gouvernance
  multi-niveaux?
\newblock {\em Cybergeo: European Journal of Geography}.

\bibitem[Murcio et~al., 2015]{murcio2015urban}
Murcio, R., Morphet, R., Gershenson, C., and Batty, M. (2015).
\newblock Urban transfer entropy across scales.
\newblock {\em PLoS One}, 10(7):e0133780.

\bibitem[Pumain, 1997]{pumain1997pour}
Pumain, D. (1997).
\newblock Pour une th{\'e}orie {\'e}volutive des villes.
\newblock {\em Espace g{\'e}ographique}, 26(2):119--134.

\bibitem[Pumain and Reuillon, 2017]{pumain2017urban}
Pumain, D. and Reuillon, R. (2017).
\newblock {\em Urban Dynamics and Simulation Models}.
\newblock Springer International.

\bibitem[Raimbault, 2018]{raimbault2018calibration}
Raimbault, J. (2018).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one}, 13(9):e0203516.

\bibitem[Raimbault, 2019a]{raimbault:halshs-02265423}
Raimbault, J. (2019a).
\newblock {Evolving accessibility landscapes: mutations of transportation
  networks in China}.
\newblock In Aveline-Dubach, N., editor, {\em {PATHWAYS OF SUSTAINABLE URBAN
  DEVELOPMENT ACROSS CHINA: THE CASES OF HANGZHOU, DATONG AND ZHUHAI}}, pages
  89--108. {Imago Editor}.
\newblock ebook.

\bibitem[Raimbault, 2019b]{raimbault:halshs-02284933}
Raimbault, J. (2019b).
\newblock {Towards integrated urban models for sustainable policies}.
\newblock In {\em {Urban analytics at the interface between environment, human
  health and behaviour}}, Shanghai, China. {Tongji University and The Alan
  Turing Institute}.

\bibitem[Raimbault, 2019c]{raimbault:halshs-02013006}
Raimbault, J. (2019c).
\newblock {Towards multi-scalar models for the co-evolution of transportation
  networks and territories}.
\newblock In {\em {Theo Quant 2019}}, Besan{\c c}on, France. {Universit{\'e} de
  Franche-Comt{\'e}}.

\bibitem[Raimbault, 2020a]{raimbault2020comparison}
Raimbault, J. (2020a).
\newblock A comparison of simple models for urban morphogenesis.
\newblock {\em arXiv preprint arXiv:2008.13277}.

\bibitem[Raimbault, 2020b]{raimbault2020hierarchy}
Raimbault, J. (2020b).
\newblock Hierarchy and co-evolution processes in urban systems.
\newblock {\em arXiv preprint arXiv:2001.11989}.

\bibitem[Raimbault, 2020c]{raimbault2020indirect}
Raimbault, J. (2020c).
\newblock Indirect evidence of network effects in a system of cities.
\newblock {\em Environment and Planning B: Urban Analytics and City Science},
  47(1):138--155.

\bibitem[Raimbault, 2020d]{raimbault2020unveiling}
Raimbault, J. (2020d).
\newblock Unveiling co-evolutionary patterns in systems of cities: a systematic
  exploration of the simpopnet model.
\newblock In {\em Theories and Models of Urbanization}, pages 261--278.
  Springer.

\bibitem[Raimbault et~al., 2020]{raimbault2020scala}
Raimbault, J., Perret, J., and Reuillon, R. (2020).
\newblock A scala library for spatial sensitivity analysis.
\newblock {\em arXiv preprint arXiv:2007.10667}.

\bibitem[Reuillon et~al., 2013]{reuillon2013openmole}
Reuillon, R., Leclaire, M., and Rey-Coyrehourcq, S. (2013).
\newblock Openmole, a workflow engine specifically tailored for the distributed
  exploration of simulation models.
\newblock {\em Future Generation Computer Systems}, 29(8):1981--1990.

\bibitem[Rozenblat and Pumain, 2018]{Rozenblat2018}
Rozenblat, C. and Pumain, D. (2018).
\newblock {\em Toward a Methodology for Multi-scalar Urban System Policies},
  pages 385--393.
\newblock Springer Singapore, Singapore.

\bibitem[Shu et~al., 2020]{shu2020modelling}
Shu, B., Zhu, S., Qu, Y., Zhang, H., Li, X., and Carsjens, G.~J. (2020).
\newblock Modelling multi-regional urban growth with multilevel logistic
  cellular automata.
\newblock {\em Computers, Environment and Urban Systems}, 80:101457.

\bibitem[Torrens and O'Sullivan, 2001]{torrens2001cellular}
Torrens, P.~M. and O'Sullivan, D. (2001).
\newblock Cellular automata and urban simulation: where do we go from here?

\bibitem[Wegener and F{\"u}rst, 2004]{wegener2004land}
Wegener, M. and F{\"u}rst, F. (2004).
\newblock Land-use transport interaction: state of the art.
\newblock {\em Available at SSRN 1434678}.

\bibitem[Wegener and Spiekermann, 2018]{wegener2018multi}
Wegener, M. and Spiekermann, K. (2018).
\newblock Multi-level urban models: Integration across space, time and
  policies.

\bibitem[White, 2006]{white2006modeling}
White, R. (2006).
\newblock Modeling multi-scale processes in a cellular automata framework.
\newblock In {\em Complex artificial environments}, pages 165--177. Springer.

\bibitem[Xu and Gao, 2019]{xu2019directional}
Xu, T. and Gao, J. (2019).
\newblock Directional multi-scale analysis and simulation of urban expansion in
  auckland, new zealand using logistic cellular automata.
\newblock {\em Computers, Environment and Urban Systems}, 78:101390.

\bibitem[Xu et~al., 2020]{xu2020urban}
Xu, T., Gao, J., Coco, G., and Wang, S. (2020).
\newblock Urban expansion in auckland, new zealand: a gis simulation via an
  intelligent self-adapting multiscale agent-based model.
\newblock {\em International Journal of Geographical Information Science},
  34(11):2136--2159.

\bibitem[Yu et~al., 2018]{yu2018modeling}
Yu, Y., He, J., Tang, W., and Li, C. (2018).
\newblock Modeling urban collaborative growth dynamics using a multiscale
  simulation model for the wuhan urban agglomeration area, china.
\newblock {\em ISPRS International Journal of Geo-Information}, 7(5):176.

\bibitem[Zhu and Tian, 2020]{zhu2020dynamic}
Zhu, J. and Tian, S. (2020).
\newblock A dynamic urban lake area evolution model based on multilevel grid,
  cellular automata, and multiagent system.
\newblock {\em Complexity}, 2020.

\end{thebibliography}

\end{document}

>>>>

\documentclass[sustainability,article,submit,moreauthors,pdftex]{Definitions/mdpi}

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{x}
\articlenumber{x}
\pubyear{2020}
\copyrightyear{2020}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line
%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%=================================================================
% Full title of the paper (Capitalized)
\Title{Strong coupling between scales in a multi-scalar model of urban dynamics}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0003-0768-9480} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Juste Raimbault $^{1,2,3,*}$\orcidA{}}

% Authors, for metadata in PDF
\AuthorNames{Juste Raimbault}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad CASA, University College London\\
$^{2}$ \quad Institut des Syst{\`e}mes Complexes Paris-Ile-de-France, CNRS\\
$^{3}$ \quad UMR G{\'e}ographie-cit{\'e}s, CNRS}

% Contact information of the corresponding author
\corres{Correspondence: juste.raimbault@polytechnique.edu}

% Current address and/or shared authorship
% \dagger,\ddagger
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%Dear Editor,

%I am pleased to submit an original research article entitled "Strong coupling between scales in a multi-scalar model of urban dynamics" for consideration for publication in IJGI. This article introduces a novel modeling study on the dynamics of urban systems, with a particular on feedbacks between scales. The subject is in my opinion furthermore particularly suited for the special issue "Spatio-Temporal Models and Geo-Technologies".

%A preliminary version of the methodology and results were presented as a main track talk at the Conference on Complex Systems 2019. A preprint was submitted on arXiv at the same date of this submission.

%I had no previous contact with journal editors regarding this manuscript. This manuscript has not been published and is not under consideration for publication elsewhere. I have no conflicts of interest to disclose. I do not have any opposed reviewer.

%Thank you for your consideration.

%Yours faithfully,

%Juste Raimbault
%University College London

\abstract{Urban evolution processes occur at different scales, with intricate interactions between levels and relatively distinct type of processes. To what extent actual urban dynamics include an actual strong coupling between scales, in the sense of both top-down and bottom-up feedbacks, remains an open issue with important practical implications for the sustainable management of territories. We introduce in this paper a multi-scalar simulation model of urban growth, coupling a system of cities interaction model at the macroscopic scale with morphogenesis models for the evolution of urban form at the scale of metropolitan areas. Strong coupling between scales is achieved through an update of model parameters at each scale depending on trajectories at the other scale. The model is applied and explored on synthetic systems of cities. Simulation results show a non-trivial effect of the strong coupling. As a consequence, an optimal action on policy parameters such as containing urban sprawl is shifted. We also run a multi-objective optimization algorithm on the model, showing showing that compromise between scales are captured. Our approach opens new research directions towards more operational urban dynamics models including a strong feedback between scales.}

% Keywords
\keyword{Urban dynamics; Systems of cities; Urban morphogenesis; Multi-scalar modeling; Strong coupling}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
%  figure: more details?
 \includegraphics[width=\linewidth]{figures/multiscale_morph.pdf}
 \caption{Schematic representation of model architecture. Urban areas with their own urban form are inserted into the macroscopic spatial interaction model, and strong coupling is achieved through top-down and bottom-up feedbacks.\label{fig:fig1}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{figures/allindics_hist.png}
	\caption{Statistical distribution of indicators for a sample of 10 parameter values.\label{fig:fig2}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{figures/onefactor_allindics_mesoMacroDecayUpdateMax_errorbars.png}
	\caption{Variations of indicators as a function of $\delta d$, when all other parameters are fixed to their nominal value.\label{fig:fig3}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{figures/deltaHierarchymacroPopulations-mesoTimeSteps_colorMacroInteractionDecay_facetmesoMacroDecayUpdateMax-macroMesoBetaUpdateMax.png}
	\caption{Macroscopic hierarchy of populations as a function of mesoscopic time steps $t_m$, for different values of interaction decay $d_G$ (colour), and of feedback parameters $\delta d$ (columns) and $\delta \beta$ (rows).\label{fig:fig4}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{figures/deltamesoMorans-macroMesoAlphaUpdateMax_colormacroMesoBetaUpdateMax_facetmesoMacroCongestionCost-mesoMacroDecayUpdateMax_mesoBeta0_11.png}
	\caption{Relative evolution of average mescoscopic Moran, as a function of feedback parameter $\delta \beta$, for different values of feedback parameter $\delta \alpha$ (colour), and of feedback parameters $\delta d$ (columns) and $\lambda$ (rows).\label{fig:fig5}}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width=\textwidth]{figures/deltamesoSlopes-macroMesoAlphaUpdateMax_colormacroMesoBetaUpdateMax_facetmesoMacroCongestionCost-mesoMacroDecayUpdateMax_mesoBeta0_11.png}
	\caption{Relative evolution of average mescoscopic population hierarchy, as a function of feedback parameter $\delta \beta$, for different values of feedback parameter $\delta \alpha$ (colour), and of feedback parameters $\delta d$ (columns) and $\lambda$ (rows).\label{fig:fig6}}
\end{figure}

\begin{figure}[h!]
	\begin{center}
	\includegraphics[width=0.6\linewidth]{figures/pareto_macroHierarchy-mesoHierarchy.png}
	\end{center}
	\caption{Pareto front obtained with a NSGA2 genetic algorithm, to minimize simultaneously hierarchy at the macroscopic and mesoscopic scales. Point size gives the number of stochastic samples and colour the value of $\delta \beta$.\label{fig:fig7}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\authorcontributions{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\funding{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{The author acknowledges the funding of their institutions and the EPSRC project number EP/M023583/1. Results obtained in this paper were computed on the vo.complex-system.eu virtual organisation of the European Grid Infrastructure (http://www.egi.eu). We thank the European Grid Infrastructure and its supporting National Grid Initiatives (France-Grilles in particular) for providing the technical support and infrastructure.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\conflictsofinterest{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

\externalbibliography{yes}
\bibliography{biblio.bib}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

%\begin{figure}[H]
%\centering
%\includegraphics[width=2 cm]{Definitions/logo-mdpi}
%\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
%\end{figure}

%\begin{table}[H]
%\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
%\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
%\begin{tabular}{ccc}
%\toprule
%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
%\midrule
%entry 1		& data			& data\\
%entry 2		& data			& data\\
%\bottomrule
%\end{tabular}
%\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\textwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\textwidth}{1pt}
%\end{listing}
